---
title: "LPA and SC"
output: html_notebook
---

```{r}
suppressPackageStartupMessages({
  library("here")
  library("tidyverse")
  library("MplusAutomation")
  library("gt")
  library("glue")
  library("kableExtra")
  library("misty")
  library("lavaan")
  library("AICcmodavg")
  library("nonnest2")
  library("DiagrammeR")
  library("lavaan")
  library("tidyLPA")
  library("semTools")
  library("brms")
  library("MBESS")
  library("ufs")
  library("robmed")
  library("careless")
  library("psych")
  library("BayesFactor")
  library("effectsize")
  library("tidybayes")
  library("emmeans")
  library("bayesplot")
  library("patchwork")
  library("bmlm")
  library("performance")
})

options("max.print" = .Machine$integer.max)

# Make random things reproducible
set.seed(1234)

options(mc.cores = 4)

bayesplot_theme_set()
```

```{r}
source(here::here("src", "R", "functions", "funs_add_neoffi60_subscales.R"))
source(here::here("src", "R", "functions", "funs_correct_iesr_scores.R"))
source(here::here("src", "R", "functions", "funs_plot_job_qualification.R"))
source(here::here("src", "R", "functions", "funs_generate_all_items_df.R"))

scale_this <- function(x) as.vector(scale(x))

sum_coding <- function(x, lvls = levels(x)) {
  # codes the first category with -1
  nlvls <- length(lvls)
  stopifnot(nlvls > 1)
  cont <- diag(nlvls)[, -nlvls, drop = FALSE]
  cont[nlvls, ] <- -1
  cont <- cont[c(nlvls, 1:(nlvls - 1)), , drop = FALSE]
  colnames(cont) <- lvls[-1]
  x <- factor(x, levels = lvls)
  contrasts(x) <- cont
  x
}
```


# Get data

```{r}
all_items <- generate_all_items_df() |> 
  ungroup()
```

There is a problem with IES-R, in the control group. I shift the control distribution of IES-R towards lower values.

```{r}
temp <- correct_iesr_scores(all_items)
all_items <- temp
```


```{r}
ggplot(all_items, aes(x = iesr_ts, colour = is_rescue_worker)) +
  geom_density()
```

```{r}
all_items |> 
  group_by(is_rescue_worker) |> 
  summarize(
    avg_iesr = mean(iesr_ts)
  )
```

There are some cases in which the RWs of Toscana and Lombardia did not have the proper qualification. They are assigned to the category of RWs.

```{r}
all_items$idx <- 1:nrow(all_items)
all_items$is_rescue_worker <- as.character(all_items$is_rescue_worker)
all_items$is_rescue_worker <- ifelse(
  all_items$idx < 746, "Si", all_items$is_rescue_worker
)
all_items$idx <- NULL
```


```{r}
all_items$commeetee_location <- ifelse(
  all_items$is_rescue_worker == "No", "None", all_items$red_cross_commeetee_location
) |> 
  factor()
```

```{r}
all_items$commeetee_location <- ifelse(
  all_items$is_rescue_worker == "No" & all_items$age < 25, "students", all_items$commeetee_location
)
```

```{r}
all_items$commeetee <- ifelse(
  all_items$is_rescue_worker == "No" & all_items$age >= 25, "community_sample",
  all_items$commeetee_location
)

all_items$commeetee <- 
  ifelse(is.na(all_items$commeetee), "community_sample", all_items$commeetee) |> 
  factor()

sum(is.na(all_items$commeetee))
```

```{r}
# all_items <- all_items %>%
#   mutate(job_qualification = case_when(
#     is_rescue_worker=="Si" & job_qualification == "non_rescue_worker" ~ "team_member",
#     TRUE ~ job_qualification)) 
```


## IES-R as a function of group

iesr_ts | trunc(lb = 0) ~ is_rescue_worker + (1 | commeetee),

```{r}
m0 <- brm(
  bf(
    iesr_ts ~ is_rescue_worker,
    sigma ~ is_rescue_worker 
    ),
  family = skew_normal(),
  data = all_items,
  backend = "cmdstanr"
)
```


```{r}
# m0 <- brm(
#   bf(
#     iesr_ts ~ is_rescue_worker + (1 | commeetee),
#     sigma ~ is_rescue_worker + (1 | commeetee)
#     ),
#   family = skew_normal(),
#   data = all_items,
#   backend = "cmdstanr"
# )
```

```{r}
pp_check(m0)
```

```{r}
summary(m0)
```

```{r}
me <- conditional_effects(
  m0, "is_rescue_worker"
)
plot(me, points = FALSE)
```

```{r}
BFt <- BayesFactor::ttestBF(
  all_items$ies_ts[all_items$is_rescue_worker == "Si"], 
  all_items$ies_ts[all_items$is_rescue_worker == "No"],
  paired = FALSE
)
effectsize(BFt)
```

Supported families are:
'acat', 'asym_laplace', 'bernoulli', 'beta', 'beta_binomial', 'binomial', 'categorical', 'com_poisson', 'cox', 'cratio', 'cumulative', 'custom', 'dirichlet', 'dirichlet2', 'discrete_weibull', 'exgaussian', 'exponential', 'frechet', 'gamma', 'gaussian', 'gen_extreme_value', 'geometric', 'hurdle_cumulative', 'hurdle_gamma', 'hurdle_lognormal', 'hurdle_negbinomial', 'hurdle_poisson', 'info', 'inverse.gaussian', 'logistic_normal', 'lognormal', 'multinomial', 'negbinomial', 'negbinomial2', 'poisson', 'shifted_lognormal', 'skew_normal', 'sratio', 'student', 'von_mises', 'weibull', 'wiener', 'zero_inflated_asym_laplace', 'zero_inflated_beta', 'zero_inflated_beta_binomial', 'zero_inflated_binomial', 'zero_inflated_negbinomial', 'zero_inflated_poisson', 'zero_one_inflated_beta'


The sk, ch, mi sub-scales are coded so that high values indicate high self-compassion levels.
The sj, is, oi sub-scales are coded so that high values indicate low self-compassion levels.

The ts_sc score has been computed by reversing the coding of the items of the sj, is, oi sub-scales (so that they indicate the absence of self-judgment, absence of isolation, absence of over-identification).

```{r}
scs_subscales <- with(all_items, data.frame(sk, ch, mi, sj, is, oi, scs_ts))
cor(scs_subscales) |> round(2)
```


## COPE scale

In the COPE scale only two factors are identified.

```{r}
all_items$pos_reinterpretation <- 
  with(all_items, cope_1 + cope_29 + cope_38 + cope_59)
all_items$mental_disengagement <- 
  with(all_items, cope_2 + cope_16 + cope_31 + cope_43) 
all_items$venting <- 
  with(all_items, cope_3 + cope_17 + cope_28 + cope_46) 
all_items$seeking_instrumental_support <- 
  with(all_items, cope_4 + cope_14 + cope_30 + cope_45) 
all_items$active_coping <- 
  with(all_items, cope_5 + cope_25 + cope_47 + cope_58)  
all_items$denial <- 
  with(all_items, cope_6 + cope_27 + cope_40 + cope_57) 
all_items$religion <- 
  with(all_items, cope_7 + cope_18 + cope_48 + cope_60) 
all_items$humor <- 
  with(all_items, cope_8 + cope_20 + cope_36 + cope_50) 
all_items$behavioral_disengagement <- 
  with(all_items, cope_9 + cope_24 + cope_37 + cope_51) 
all_items$restraint <- 
  with(all_items, cope_10 + cope_22 + cope_41 + cope_49) 
all_items$seeking_emotional_support <- 
  with(all_items, cope_11 + cope_23 + cope_34 + cope_52) 
all_items$substance_use <- 
  with(all_items, cope_12 + cope_26 + cope_35 + cope_53) 
all_items$acceptance <- 
  with(all_items, cope_13 + cope_21 + cope_44 + cope_54) 
all_items$suppr_competing_activities <- 
  with(all_items, cope_15 + cope_33 + cope_42 + cope_55) 
all_items$planning <- 
  with(all_items, cope_19 + cope_32 + cope_39 + cope_56) 
```

Create COPE sub-scales scores using *all* items -- note that SEM analyses suggest 
to drop some of the items.

```{r}
all_items$active_coping <- with(
  all_items, pos_reinterpretation + active_coping +
  suppr_competing_activities + planning + restraint + 
    seeking_instrumental_support + acceptance
)

all_items$avoidance_coping <- with(
  all_items, mental_disengagement + denial + humor +
  behavioral_disengagement + substance_use + religion 
)

all_items$soc_emo_coping <- with(
  all_items, seeking_instrumental_support +
  seeking_emotional_support + venting
)
```


## Self-compassion scale


```{r}
plot(density(all_items$scs_ts))
```


```{r}
fit_1 <- brm(
  bf(
    scs_ts ~ is_rescue_worker,
    sigma ~ is_rescue_worker
    ),
  family = student(),
  backend = "cmdstanr",
  data = all_items
)
```

```{r}
pp_check(fit_1)
```


```{r}
me <- conditional_effects(
  fit_1, "is_rescue_worker"
)
plot(me, points = FALSE)
```

```{r}
summary(fit_1)
```

```{r}
BFt <- BayesFactor::ttestBF(
  all_items$scs_ts[all_items$is_rescue_worker == "Si"], 
  all_items$scs_ts[all_items$is_rescue_worker == "No"],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
rw_df <- all_items |> 
  dplyr::filter(is_rescue_worker == "Si")

rw_df <- rw_df %>%
  mutate(job_qualification = case_when(
    job_qualification == "non_rescue_worker" ~ "team_member",
    TRUE ~ job_qualification))
```


## Preliminary EFA

Preliminary ESEM analysis is performed in script 04_esem_within_cfa.R.


## LPA

```{r}
lpa_scales <- c(
  "is_rescue_worker",
  "neuroticism", "extraversion", "openness", "agreeableness", "conscientiousness",
  "active_coping", "avoidance_coping", "soc_emo_coping",
  "iesr_ts",
  # "avoiding", "intrusivity", "hyperarousal",
  # "sk", "ch", "mi", "sj", "is", "oi",
  # "pos_sc",
  # "neg_sc",
  # "ts_sc",
  "mpss_tot"
  # "ptgi_total_score"
  # "relating_to_others",
  # "new_possibilities",
  # "personal_strength",
  # "appreciation_of_life",
  # "spirituality"
)
```

Select only the relevant variables

```{r}
lpa_rw_df <- rw_df |> 
  dplyr::select(all_of(lpa_scales)) 

lpa_rw_df$is_rescue_worker <- NULL
```


```{r}
check_outliers(lpa_rw_df) 
```

```{r}
lpa_rw_clean_df <- lpa_rw_df[-c(132, 309, 431, 454, 455, 612, 750, 751), ]
rw_clean_df <- rw_df[-c(132, 309, 431, 454, 455, 612, 750, 751), ]
```

```{r}
psych::describe(lpa_rw_clean_df)
```

```{r}
lpa_rw_clean_df %>% 
  scale() %>%
  estimate_profiles(1:6,
    variances = c("equal", "varying"),
    covariances = c("zero", "varying"),
    package = "MplusAutomation"
  )
```

 Model Classes AIC      BIC      Entropy prob_min prob_max n_min n_max BLRT_p
 1     1       21200.56 21292.85 1.00    1.00     1.00     1.00  1.00        
 1     2       20604.04 20747.10 0.71    0.87     0.94     0.36  0.64  0.00  
 1     3       20322.46 20516.27 0.75    0.82     0.93     0.18  0.56  0.00  
 1     4       20180.65 20425.23 0.74    0.83     0.86     0.10  0.42  0.00  
 1     5       20066.42 20361.76 0.74    0.79     0.88     0.08  0.34  0.00  
 1     6       20007.30 20353.40 0.73    0.76     0.86     0.06  0.30  0.00  
 1     7       19941.06 20337.92 0.76    0.77     0.85     0.03  0.31  0.00  
 1     8       19877.85 20325.48 0.78    0.74     0.88     0.02  0.30  0.00  
 1     9       19826.21 20324.60 0.78    0.75     0.91     0.02  0.33  0.00  
 1     10      19793.42 20342.58 0.78    0.75     0.92     0.01  0.33  0.00  
 6     1       19747.98 20047.94 1.00    1.00     1.00     1.00  1.00        
 6     2       19380.08 19984.61 0.70    0.89     0.94     0.45  0.55  0.00  
 6     3       19286.96 20196.06 0.74    0.88     0.89     0.23  0.39  0.00  
 6     4       19262.78 20476.45 0.78    0.83     0.93     0.11  0.43  1.00  
 6     5       19282.17 20800.41 0.78    0.81     0.92     0.07  0.43  0.43  
 6     6       19257.62 21080.44 0.86    0.83     1.00     0.03  0.51  0.00  
 6     7       19211.10 21338.49 0.84    0.78     1.00     0.01  0.47        
 6     8       19629.33 22061.29 0.86    0.00     0.95     0.00  0.53        
 6     9                                                                     
 6     10      19648.29 22675.55 0.87    0.00     1.00     0.00  0.42     

```{r}
lpa_rw_clean_df %>% 
  scale() %>%
  estimate_profiles(1:3,
    variances = c("equal", "varying"),
    covariances = c("zero", "varying"),
    package = "MplusAutomation"
  ) %>% 
  compare_solutions(statistics = c("AIC", "BIC"))
```

Compare tidyLPA solutions:

 Model Classes AIC       BIC      
 1     1       21342.450 21434.878
 1     2       20746.522 20889.786
 1     3       20464.673 20658.772
 1     4       20341.265 20586.199
 1     5       20245.437 20541.207
 1     6       20175.056 20521.661
 6     1       19889.997 20190.388
 6     2       19515.286 20120.691
 6     3       19437.181 20347.598
 6     4       19389.596 20605.025
 6     5       19400.107 20920.550
 6     6       19404.469 21229.925

Best model according to AIC is Model 6 with 4 classes.
Best model according to BIC is Model 6 with 2 classes.

An analytic hierarchy process, based on the fit indices AIC, AWE, BIC, CLC, and KIC (Akogul & Erisoglu, 2017), suggests the best solution is Model 6 with 2 classes.


```{r}
m2 <- lpa_rw_clean_df %>%
  scale() %>%
  estimate_profiles(2,
    variances = "varying",
    covariances = "varying",
    package = "MplusAutomation"
  )
```


```{r}
m2_plot <- lpa_rw_clean_df %>%
  scale() %>%
  estimate_profiles(2,
    variances = "varying",
    covariances = "varying",
    package = "MplusAutomation"
    ) %>%
    plot_profiles(add_line = TRUE, rawdata= FALSE, bw = FALSE)
```

Profile 2: dysfunctional
Profile 1: adaptive


```{r}
get_estimates(m2)
```

```{r}
out <- get_data(m2)
rw_clean_df$class_num <- out$Class
```

```{r}
table(
  rw_clean_df$class_num
)
```


```{r}
table(
  rw_clean_df$class_num, rw_clean_df$job_qualification
)
```


```{r}
rw_clean_df$class <- factor(rw_clean_df$lpa_class)
summary(rw_clean_df$class)
```

```{r}
# Select relevant variables for LPA covariate analysis.
temp <- lpa_rw_clean_df
# temp$class_num <- out$Class
temp$scs <- rw_clean_df$scs_ts

rio::export(
  temp,
  here::here("data", "processed", "lpa", "lpa_final.csv")
)

rm(temp)
```



```{r}
m1 <- brm(
  bf(scs_ts ~ class),
  family = student(),
  data = rw_clean_df,
  init = 0.1,
  backend = "cmdstanr",
  adapt_delta = 0.9
)
```

```{r}
pp_check(m1)
```


```{r}
summary(m1)
```

```{r}
me <- conditional_effects(
  m1, "class"
)
plot(me, points = FALSE)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$scs_ts[rw_df$class == 1], 
  rw_df$scs_ts[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt, type = "d")
```

```{r}
m1 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  labs(x = "LPA Class", y = "SCS Score", title = "Rescue Workers") +
  papaja::theme_apa() + 
  annotate("text", x = 1, y = 78.5, label = "Bayesian Cohen's d = 0.89\n 95% CI [0.73, 1.04]")
```




```{r}
names(all_items)
```

### Self-judgment

```{r}
m2 <- brm(
  bf(sj ~ class),
  data = rw_df,
  family = student,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m2)
```

```{r}
summary(m2)
```


```{r}
me <- conditional_effects(
  m2, "class"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m2, specs = pairwise ~ class)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$sj[rw_df$class == 1], 
  rw_df$sj[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```


```{r}
p2 <- m2 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Self-Judgment", title = "A") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 16, label = "Bayesian Cohen's d = 0.82\n 95% CI [0.67, 0.97]")
p2
```

### Isolation

```{r}
m3 <- brm(
  bf(is ~ class),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m3)
```

```{r}
summary(m3)
```


```{r}
me <- conditional_effects(
  m3, "class"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m3, specs = pairwise ~ class)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$is[rw_df$class == 1], 
  rw_df$is[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
p3 <- m3 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Isolation", title = "B") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 11, label = "Bayesian Cohen's d = 0.94\n 95% CI [0.79, 1.10]")
p3
```

### Over-identification


```{r}
m4 <- brm(
  bf(oi ~ class),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m4)
```

```{r}
summary(m4)
```


```{r}
me <- conditional_effects(
  m4, "class"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m4, specs = pairwise ~ class)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$oi[rw_df$class == 1], 
  rw_df$oi[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
p4 <- m4 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('High Resilience', 'Low Resilience')) +
  labs(x = "LPA Class", y = "SCS Over-Identification", title = "C") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 9.4, label = "Bayesian Cohen's d = 0.97\n 95% CI [0.82, 1.12]")
p4
```


### Self-kindness

```{r}
m5 <- brm(
  bf(sk ~ class),
  family = student(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m5)
```

```{r}
summary(m5)
```


```{r}
me <- conditional_effects(
  m5, "class"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m5, specs = pairwise ~ class)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$sk[rw_df$class == 1], 
  rw_df$sk[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
p5 <- m5 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('High Resilience', 'Low Resilience')) +
  labs(x = "LPA Class", y = "SCS Self-Kindness", title = "D") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 14.5, label = "Bayesian Cohen's d = 0.28\n 95% CI [0.14, 0.43]")
p5
```

### Common humanity

```{r}
m6 <- brm(
  bf(ch ~ class),
  family = student(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m6)
```

```{r}
summary(m6)
```


```{r}
me <- conditional_effects(
  m6, "class"
)
plot(me, points = FALSE)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$ch[rw_df$class == 1], 
  rw_df$ch[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```


```{r}
p6 <- m6 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('High Resilience', 'Low Resilience')) +
  labs(x = "LPA Class", y = "SCS Common-Humanity", title = "E") +
  # papaja::theme_apa() + 
  annotate("text", x = 1.5, y = 12.3, label = "Bayesian Cohen's d = 0.00\n 95% CI [-0.14, 0.14]")
p6
```

### Mindfulness

```{r}
m7 <- brm(
  bf(mi ~ class),
  family = student(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m7)
```

```{r}
summary(m7)
```

```{r}
emmeans(m7, specs = pairwise ~ class)
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$mi[rw_df$class == 1], 
  rw_df$mi[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
me <- conditional_effects(
  m7, "class"
)
plot(me, points = FALSE)
```


```{r}
p7 <- m7 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "SCS Mindfulness", title = "F") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 13.8, label = "Bayesian Cohen's d = 0.32\n 95% CI [0.17, 0.46]")
p7
```

```{r}
fig_scs <- (p2 | p3 | p4) /
(p5 | p6 | p7)

out <- fig_scs + plot_annotation(
  title = 'SCS Subscales as a Function of LPA Class',
  subtitle = 'Rescue Workers group'
  # caption = 'Disclaimer: None of these plots are insightful'
)
ggsave("scs_subscales_lpa.pdf", width = 35, height = 20, units = "cm")
```

## IES-R

```{r}
m10 <- brm(
  bf(ies_ts ~ class),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m10)
```

```{r}
summary(m10)
```

```{r}
p10 <- m10 %>%
  emmeans( ~ class) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = class, y = .value)) +
  geom_eye() +
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  # facet_grid(~ wool) +
  # theme_light()
  scale_x_discrete(labels=c('Low Resilience', 'High Resilience')) +
  labs(x = "LPA Class", y = "Impact of Event Scale - Revised (IES-R)") +
  # papaja::theme_apa() + 
  annotate("text", x = 1, y = 17, label = "Bayesian Cohen's d = 1.34\n 95% CI [1.18, 1.50]")
p10
```

```{r}
BFt <- BayesFactor::ttestBF(
  rw_df$ies_ts[rw_df$class == 1], 
  rw_df$ies_ts[rw_df$class == 2],
  paired = FALSE
)
effectsize(BFt)
```

```{r}
emmeans(m10 , specs = pairwise ~ class)
```


```{r}
m11 <- brm(
  bf(ptgi_total_score | trunc(lb = 0) ~ class),
  family = student(),
  data = rw_df,
  backend = "cmdstanr"
)
```

```{r}
pp_check(m11)
```

```{r}
summary(m11)
```

### Job qualification

```{r}
rw_df$job_qualification <- ifelse(
  rw_df$job_qualification == "non_rescue_worker", "team_member", 
  rw_df$job_qualification
) 
```


```{r}
m12 <- brm(
  bf(ies_ts ~ job_qualification),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m12)
```

```{r}
summary(m12)
```

```{r}
me <- conditional_effects(
  m12, "job_qualification"
)
plot(me, points = FALSE)
```

```{r}
emmeans(m12 , specs = pairwise ~ job_qualification)
```

```{r}
m13 <- brm(
  bf(scs_ts ~ job_qualification * class),
  family = gaussian(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m13)
```

```{r}
me <- conditional_effects(
  m13, "job_qualification:class"
)
plot(me, points = FALSE)
```

```{r}
summary(m13)
```

```{r}
emmeans(m13 , specs = pairwise ~ job_qualification*class)
```

```{r}
m14 <- brm(
  bf(ptgi_total_score ~ ies_total_score | (1 | comme\)),
  family = gaussian(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
summary(m14)
```
```{r}
bayes_R2(m14)
```
```{r}
conditional_effects(m14, "is:class")
```


## SEM

```{r}
mydf <- data.frame(
  scs = scale(rw_df$scs_ts),
  class = ifelse(rw_df$class == 1, 0.0, 1.0),
  ptgi = scale(rw_df$ptgi_total_score),
  psc = scale(rw_df$sk + rw_df$ch + rw_df$mi),
  nsc = scale(rw_df$sj + rw_df$oi + rw_df$is),
  commettee = rw_df$red_cross_commeetee_location,
  id = 1:nrow(rw_df)
)

mydf <- mydf[complete.cases(mydf), ]
```

```{r}
# Impute NAs with the mode.
# mydf$commettee[is.na(mydf$commettee)] <- "Comitato di Groane"
# summary(factor(mydf$commettee))
```


```{r}
f1 <- bf(scs ~ class, family = skew_normal())
f2 <- bf(ptgi ~ scs + class, family = skew_normal())
mod <- brm(
  f1 + f2 + set_rescor(FALSE), 
  data = mydf, 
  cores = 4, 
  refresh = 0,
  init = 0.1,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
bayestestR::mediation(mod, mediator = "scs", ci = 0.95, method = "SPI")
```

```{r}
pp_check(mod, resp = "ptgi")
```

```{r}
pp_check(mod, resp = "scs")
```

```{r}
summary(mod)
```

```{r}
fit <- mlm(d = mydf, 
           id = "commettee",
           x = "class",
           m = "scs",
           y = "ptgi",
           iter = 2000, 
           cores = 4)
```

```{r}
mlm_path_plot(fit, level = .95, text = T,
              xlab = "Resilience\nProfile",
              mlab = "Self\nCompassion",
              ylab = "PTG", digits = 2)
```

# Causal Mediation Analysis for Stan Model

  Treatment: class
  Mediator : scs
  Response : ptgi

Effect                 | Estimate |          95% SPI
----------------------------------------------------
Direct Effect (ADE)    |   -0.300 | [-0.464, -0.140]
Indirect Effect (ACME) |    0.121 | [ 0.053,  0.187]
Mediator Effect        |    0.154 | [ 0.069,  0.230]
Total Effect           |   -0.178 | [-0.325, -0.027]




```{r}
m16 <- brm(
  bf(ptgi_total_score ~ class),
  family = skew_normal(),
  data = rw_df,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
pp_check(m16)
```


```{r}
summary(m16)
```

```{r}
bayes_R2(m16)
```

```{r}
m17 <- brm(
  bf(ptgi_total_score ~ is_rescue_worker),
  family = skew_normal(),
  data = all_items,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```


```{r}
summary(m17)
```

```{r}
rw_df$rate_of_activity_num <- as.integer(rw_df$rate_of_activity_num)
```


```{r}
temp <- rw_df[1:746, ]

temp$activity <- cut(
  temp$rate_of_activity_num,
  breaks = c(-1, 0, 1, 2),    
  labels = c("Low", "Medium", "High"),   
  include.lowest = TRUE,    
  ordered_result = TRUE
)   
```

```{r}
m19 <- brm(
  bf(activity ~ class),
  family=cumulative("logit"),
  data = temp,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```


```{r}
pp_check(m19)
```


```{r}
summary(m19)
```

```{r}
m20 <- brm(
  bf(class ~ last_training_num * scs_ts),
  family=bernoulli(),
  data = temp,
  backend = "cmdstanr",
  adapt_delta = 0.99
)
```

```{r}
summary(m20)
```

```{r}
conditional_effects(m20, "scs_ts:last_training_num")
```


```{r}
table(rw_df$class, rw_df$last_training_num)
```

