---
title: "LPA and SC"
output: html_notebook
---

COPE

We are interested in how people respond when they confront difficult or stressful events in their lives. There are lots of ways to try to deal with stress.  This questionnaire asks you to indicate what you generally do and feel, when you experience stressful events.  Obviously, different events bring out somewhat different responses, but think about what you usually do when you are under a lot of stress.

Then respond to each of the following items by blackening one number on your answer sheet for each, using the response choices listed just below.  Please try to respond to each item separately in your mind from each other item.  Choose your answers thoughtfully, and make your answers as true FOR YOU as you can.  Please answer every item.  There are no "right" or "wrong" answers, so choose the most accurate answer for YOU--not what you think "most people" would say or do.  Indicate what YOU usually do when YOU experience a stressful event.

       1 = I usually don't  do this at all
       2 = I usually do this a little bit
       3 = I usually do this a medium amount
       4 = I usually do this a lot

1.  I try to grow as a person as a result of the experience.
2.  I turn to work or other substitute activities to take my mind off things.
3.  I get upset and let my emotions out.
4.  I try to get advice from someone about what to do.
5.  I concentrate my efforts on doing something about it.
6.  I say to myself "this isn't real."
7.  I put my trust in God.
8.  I laugh about the situation.
9.  I admit to myself that I can't deal with it, and quit trying.
10.  I restrain myself from doing anything too quickly.

11.  I discuss my feelings with someone.
12.  I use alcohol or drugs to make myself feel better.
13.  I get used to the idea that it happened.
14.  I talk to someone to find out more about the situation.
15.  I keep myself from getting distracted by other thoughts or activities.
16.  I daydream about things other than this.
17.  I get upset, and am really aware of it.
18.  I seek God's help.
19.  I make a plan of action.
20.  I make jokes about it.

21.  I accept that this has happened and that it can't be changed.
22.  I hold off doing anything about it until the situation permits.
23.  I try to get emotional support from friends or relatives.
24.  I just give up trying to reach my goal.
25.  I take additional action to try to get rid of the problem.
26.  I try to lose myself for a while by drinking alcohol or taking drugs.
27.  I refuse to believe that it has happened.
28.  I let my feelings out.
29.  I try to see it in a different light, to make it seem more positive.
30.  I talk to someone who could do something concrete about the problem.

31.  I sleep more than usual.
32.  I try to come up with a strategy about what to do.
33.  I focus on dealing with this problem, and if necessary let other things slide a little.
34.  I get sympathy and understanding from someone.
35.  I drink alcohol or take drugs, in order to think about it less.
36.  I kid around about it.
37.  I give up the attempt to get what I want.
38.  I look for something good in what is happening.
39.  I think about how I might best handle the problem.
40.  I pretend that it hasn't really happened.

41.  I make sure not to make matters worse by acting too soon.
42.  I try hard to prevent other things from interfering with my efforts at dealing with this.
43.  I go to movies or watch TV, to think about it less.
44.  I accept the reality of the fact that it happened.
45.  I ask people who have had similar experiences what they did.
46.  I feel a lot of emotional distress and I find myself expressing those feelings a lot.
47.  I take direct action to get around the problem.
48.  I try to find comfort in my religion.
49.  I force myself to wait for the right time to do something.
50.  I make fun of the situation.

51.  I reduce the amount of effort I'm putting into solving the problem.
52.  I talk to someone about how I feel.
53.  I use alcohol or drugs to help me get through it.
54.  I learn to live with it.
55.  I put aside other activities in order to concentrate on this.
56.  I think hard about what steps to take.
57.  I act as though it hasn't even happened.
58.  I do what has to be done, one step at a time.
59.  I learn something from the experience.
60.  I pray more than usual.

------------------------------------------------------------------------

Scales (sum items listed, with no reversals of coding):

Positive reinterpretation and growth:  1, 29, 38, 59
Mental disengagement:  2, 16, 31, 43
Focus on and venting of emotions:  3, 17, 28, 46
Use of instrumental social support:  4, 14, 30, 45
Active coping:  5, 25, 47, 58
Denial:  6, 27, 40, 57
Religious coping:  7, 18, 48, 60
Humor:  8, 20, 36, 50
Behavioral disengagement:  9, 24, 37, 51
Restraint:  10, 22, 41, 49
Use of emotional social support:  11, 23, 34, 52
Substance use:  12, 26, 35, 53
Acceptance:  13, 21, 44, 54
Suppression of competing activities:  15, 33, 42, 55
Planning:  19, 32, 39, 56

```{r}
library("here")
library("tidyverse")
library("MplusAutomation")
library("gt")
library("glue")
library("kableExtra")
library("misty")
library("lavaan")
library("AICcmodavg")
library("nonnest2")
library("DiagrammeR")
library("lavaan")
library("tidyLPA")
library("semTools")
library("brms")
library("MBESS")
library("ufs")
library("robmed")
library("careless")
library("psych")

options("max.print" = .Machine$integer.max)

# Make random things reproducible
set.seed(1234)

options(
  mc.cores = 6 # Use 6 cores
)

source(here::here("src", "R", "functions", "funs_add_neoffi60_subscales.R"))
source(here::here("src", "R", "functions", "funs_correct_iesr_scores.R"))
source(here::here("src", "R", "functions", "funs_plot_job_qualification.R"))
source(here::here("src", "R", "functions", "funs_generate_all_items_df.R"))

scale_this <- function(x) as.vector(scale(x))
```

# Get data

```{r}
all_items <- generate_all_items_df()
```

There is a problem with IES-R, in the control group. I shift the control distribution of IES-R towards lower values.

```{r}
all_items$ies_ts <- NULL
temp <- correct_iesr_scores(all_items)
all_items <- temp
```

Compute IES-R total score.

```{r}
all_items$iesr_ts <- with(
  all_items,
  ies_1 + ies_2 + ies_3 + ies_4 + ies_5 + ies_6 + ies_7 + ies_8 + ies_9 + 
    ies_10 + ies_11 + ies_12 + ies_13 + ies_14 + ies_15 + ies_16 + ies_17 + 
    ies_18 + ies_19 + ies_20 + ies_21 + ies_22 
)
```


```{r}
ggplot(all_items, aes(x = iesr_ts, colour = is_rescue_worker)) +
  geom_density()
```


```{r}
all_items |> 
  group_by(is_rescue_worker) |> 
  summarize(
    avg_iesr = mean(iesr_ts)
  )
```

Supported families are:
'acat', 'asym_laplace', 'bernoulli', 'beta', 'beta_binomial', 'binomial', 'categorical', 'com_poisson', 'cox', 'cratio', 'cumulative', 'custom', 'dirichlet', 'dirichlet2', 'discrete_weibull', 'exgaussian', 'exponential', 'frechet', 'gamma', 'gaussian', 'gen_extreme_value', 'geometric', 'hurdle_cumulative', 'hurdle_gamma', 'hurdle_lognormal', 'hurdle_negbinomial', 'hurdle_poisson', 'info', 'inverse.gaussian', 'logistic_normal', 'lognormal', 'multinomial', 'negbinomial', 'negbinomial2', 'poisson', 'shifted_lognormal', 'skew_normal', 'sratio', 'student', 'von_mises', 'weibull', 'wiener', 'zero_inflated_asym_laplace', 'zero_inflated_beta', 'zero_inflated_beta_binomial', 'zero_inflated_binomial', 'zero_inflated_negbinomial', 'zero_inflated_poisson', 'zero_one_inflated_beta'


The sk, ch, mi sub-scales are coded so that high values indicate high self-compassion levels.
The sj, is, oi sub-scales are coded so that high values indicate low self-compassion levels.

The ts_sc score has been computed by reversing the coding of the items of the sj, is, oi sub-scales (so that they indicate the absence of self-judgment, absence of isolation, absence of over-identification).

```{r}
scs_subscales <- with(all_items, data.frame(sk, ch, mi, sj, is, oi, ts_sc))
cor(scs_subscales) |> round(2)
```


## COPE scale

In the COPE scale only two factors are identified.

```{r}
all_items$pos_reinterpretation <- with(all_items, cope_1 + cope_29 + cope_38 + cope_59)
all_items$mental_disengagement <- with(all_items, cope_2 + cope_16 + cope_31 + cope_43) 
all_items$venting <- with(all_items, cope_3 + cope_17 + cope_28 + cope_46) 
all_items$seeking_instrumental_support <- with(all_items, cope_4 + cope_14 + cope_30 + cope_45) 
all_items$active_coping <- with(all_items, cope_5 + cope_25 + cope_47 + cope_58)  
all_items$denial <- with(all_items, cope_6 + cope_27 + cope_40 + cope_57) 
all_items$religion <- with(all_items, cope_7 + cope_18 + cope_48 + cope_60) 
all_items$humor <- with(all_items, cope_8 + cope_20 + cope_36 + cope_50) 
all_items$behavioral_disengagement <- with(all_items, cope_9 + cope_24 + cope_37 + cope_51) 
all_items$restraint <- with(all_items, cope_10 + cope_22 + cope_41 + cope_49) 
all_items$seeking_emotional_support <- with(all_items, cope_11 + cope_23 + cope_34 + cope_52) 
all_items$substance_use <- with(all_items, cope_12 + cope_26 + cope_35 + cope_53) 
all_items$acceptance <- with(all_items, cope_13 + cope_21 + cope_44 + cope_54) 
all_items$suppr_competing_activities <- with(all_items, cope_15 + cope_33 + cope_42 + cope_55) 
all_items$planning <- with(all_items, cope_19 + cope_32 + cope_39 + cope_56) 
```

Create COPE sub-scales scores using *all* items -- note that SEM analyses suggest 
to drop some of the items.

```{r}
all_items$active_coping <- with(
  all_items, pos_reinterpretation + active_coping +
  suppr_competing_activities + planning + restraint + 
    seeking_instrumental_support + acceptance
)

all_items$avoidance_coping <- with(
  all_items, mental_disengagement + denial + humor +
  behavioral_disengagement + substance_use + religion 
)

all_items$soc_emo_coping <- with(
  all_items, seeking_instrumental_support +
  seeking_emotional_support + venting
)
```


## Self-compassion scale


```{r}
library("brms")
```


```{r}
plot(density(all_items$ts_sc))
```


```{r}
fit_1 <- brm(
  ts_sc ~ is_rescue_worker,
  family = student(),
  backend = "cmdstanr",
  data = all_items
)
```

```{r}
pp_check(fit_1)
```


```{r}
me <- conditional_effects(
  fit_1, "is_rescue_worker"
)
plot(me, points = FALSE)
```

```{r}
summary(fit_1)
```



## LPA


```{r}
lpa_scales <- c(
  # "is_rescue_worker",
  "neuroticism", "extraversion", "openness", "agreeableness", "conscientiousness",
  "active_coping", "avoidance_coping", "soc_emo_coping",
  "iesr_ts",
  # "sk", "ch", "mi", "sj", "is", "oi",
  # "pos_sc",
  # "neg_sc",
  # "ts_sc",
  "mpss_tot",
  "ptgi_total_score"
  # "relating_to_others",
  # "new_possibilities",
  # "personal_strength",
  # "appreciation_of_life",
  # "spirituality"
)

lpa_df <- subset(all_items, select=lpa_scales)
```

## LPA

Only RW

```{r}
rw_df <- all_items |> 
  dplyr::filter(is_rescue_worker == "yes")

lpa_rw_df <- subset(rw_df, select=lpa_scales)
```

I tried with only the RW data. The LPA produces a 2 classes solution. However, the classes are less interpretable than those found when the data of all two groups are used. So, it is better to use all the data for the LPA.

```{r}
lpa_df %>% 
  scale() %>%
  estimate_profiles(1:10,
    variances = c("equal", "varying"),
    covariances = c("zero", "varying"),
    # package = "MplusAutomation"
  ) %>% 
  compare_solutions(statistics = c("AIC", "BIC"))
```

Compare tidyLPA solutions:

 Model Classes AIC       BIC      
 1     1       86371.720 86481.034
 1     2       85170.836 85339.776
 1     3       84750.979 84979.546
 1     4       84266.489 84554.683
 1     5       84119.416 84467.235
 1     6       84012.505 84419.951
 1     7       83871.894 84338.966
 1     8       83848.135 84374.833
 1     9       83774.673 84360.997
 1     10      83627.711 84273.661
 6     1       84148.600 84531.202
 6     2       83350.747 84120.919
 6     3       82934.273 84092.015
 6     4       82866.542 84411.855
 6     5       82811.110 84743.992
 6     6       82751.355 85071.809
 6     7       82683.505 85391.528
 6     8       82709.839 85805.433
 6     9       82802.128 86285.292
 6     10      82813.820 86684.554

Best model according to AIC is Model 6 with 7 classes.
Best model according to BIC is Model 6 with 3 classes.

An analytic hierarchy process, based on the fit indices AIC, AWE, BIC, CLC, and KIC (Akogul & Erisoglu, 2017), suggests the best solution is Model 6 with 3 classes.


Varying variances and varying covariances (Model 6)



```{r}
m2 <- lpa_df %>%
  # scale() %>%
  estimate_profiles(3,
    variances = "varying",
    covariances = "varying"
    # package = "MplusAutomation"
  )
```


```{r}
temp <- lpa_df
temp$lpa_class <- NULL

m2_plot <- temp %>%
  scale() %>%
  estimate_profiles(2,
    variances = "varying",
    covariances = "varying",
    package = "MplusAutomation"
    ) %>%
    plot_profiles()
```

Profile 1: adaptive
Profile 2: dysfunctional
Profile 3: adaptive under duress (high IES scores, low MSPSS scores)


```{r}
get_estimates(m2)
```



```{r}
out <- get_data(m2)
lpa_df$lpa_class <- out$Class
```

```{r}
table(
  lpa_df$lpa_class, all_items$is_rescue_worker
)
```

```{r}
1 - (455 + 249) / (455 + 249 + 42)
# [1] 0.9436997
```

```{r}
181 / (181 + 47 + 94)
```

```{r}
table(
  lpa_df$lpa_class, all_items$job_qualification
)
```


```{r}
all_items$class <- factor(lpa_df$lpa_class)
```

```{r}
m1 <- brm(
  ts_sc ~ class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m1)
```


```{r}
summary(m1)
```

```{r}
me <- conditional_effects(
  m1, "class"
)
plot(me, points = FALSE)
```


```{r}
names(all_items)
```



```{r}
m2 <- brm(
  sj ~ job_qualification * class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m2)
```


```{r}
summary(m2)
```


```{r}
me <- conditional_effects(
  m2, "job_qualification:class"
)
plot(me, points = FALSE)
```



```{r}
m3 <- brm(
  is ~ job_qualification * class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m3)
```

```{r}
me <- conditional_effects(
  m3, "job_qualification:class"
)
plot(me, points = FALSE)
```


```{r}
m4 <- brm(
  oi ~ job_qualification*class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m4)
```

```{r}
me <- conditional_effects(
  m4, "job_qualification:class"
)
plot(me, points = FALSE)
```



```{r}
m5 <- brm(
  sk ~ job_qualification*class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m5)
```

```{r}
me <- conditional_effects(
  m5, "job_qualification:class"
)
plot(me, points = FALSE)
```



```{r}
m6 <- brm(
  ch ~ job_qualification*class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m6)
```

```{r}
me <- conditional_effects(
  m6, "job_qualification:class"
)
plot(me, points = FALSE)
```



```{r}
m7 <- brm(
  mi ~ job_qualification*class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m7)
```

```{r}
me <- conditional_effects(
  m7, "job_qualification:class"
)
plot(me, points = FALSE)
```

Profilo 2: disfunzionale
Profilo 1: adattivo
Profilo 3: adattivo con stress

```{r}
m8 <- brm(
  sj ~ class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m8)
```

```{r}
me <- conditional_effects(
  m8, "class"
)
plot(me, points = FALSE)
```


```{r}
m9 <- brm(
  is ~ class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m9)
```

```{r}
me <- conditional_effects(
  m9, "class"
)
plot(me, points = FALSE)
```


```{r}
m10 <- brm(
  oi ~ class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m10)
```

```{r}
me <- conditional_effects(
  m10, "class"
)
plot(me, points = FALSE)
```




```{r}
m11 <- brm(
  sk ~ class,
  data = all_items,
  backend = "cmdstanr",
)
```

```{r}
pp_check(m11)
```

```{r}
me <- conditional_effects(
  m11, "class"
)
plot(me, points = FALSE)
```


## Ordinal regression

```{r}
rw_df <- all_items |> 
  dplyr::filter(is_rescue_worker == "yes")
```

```{r}
rw_df$job_qualification <- factor(
  rw_df$job_qualification,
  order = TRUE,
  levels = c("driver", "team_leader", "team_member")
)
```


```{r}
fit_sc1 <- brm(
formula = job_qualification ~ 1 + class, data = rw_df,
family = cumulative("probit")
)

```

```{r}
marginal_effects(fit_sc1, "class", categorical = TRUE)
```

```{r}
summary(fit_sc1)
```



```{r}
all_items_clean <- all_items[!temp1$FLAG, ]
```

```{r}
all_items_clean$class <- lpa_clean$lpa_class - 1
```


```{r}
m1 <- brm(
  class ~ is_rescue_worker,
  family = bernoulli(),
  backend = "cmdstanr",
  all_items_clean
)
```

```{r}
pp_check(m1)
```

```{r}
summary(m1)
```

```{r}
conditional_effects(
  m1, "is_rescue_worker"
)
```


```{r}
model_glm = glm(class ~ is_rescue_worker, data = all_items_clean, family = "binomial")
```

```{r}
model_glm_pred = ifelse(predict(model_glm, type = "link") > 0, "Yes", "No")
```

```{r}
all_items_clean$class_lpa <- ifelse(all_items_clean$class == 1, "Yes", "No")
```


```{r}
train_tab = table(predicted = model_glm_pred, actual = all_items_clean$class_lpa)
library(caret)
train_con_mat = confusionMatrix(train_tab, positive = "Yes")
c(train_con_mat$overall["Accuracy"], 
  train_con_mat$byClass["Sensitivity"], 
  train_con_mat$byClass["Specificity"])
```

```{r}
library(pROC)
test_prob = predict(model_glm, newdata = all_items_clean, type = "response")

```


```{r}
all_items_clean$rw <- ifelse(
  all_items_clean$is_rescue_worker == "yes", 1, 0
)

test_roc = roc(all_items_clean$class_lpa ~ all_items_clean$rw, plot = TRUE, print.auc = TRUE)
```

```{r}
as.numeric(test_roc$auc)
```


```{r}
summary(model_glm)
```









```{r}
all_items$last_training <- ifelse(
  is.na(all_items$last_training), 0, all_items$last_training
)

all_items$rate_of_activity <- ifelse(
  is.na(all_items$rate_of_activity), 0, all_items$rate_of_activity
)

all_items$is_job_qualification_invariant <- ifelse(
  all_items$is_job_qualification_invariant == "Sì" | all_items$is_job_qualification_invariant == "Si", 
  "Yes", all_items$is_job_qualification_invariant
)

all_items$is_job_qualification_invariant <- ifelse(
  is.na(all_items$is_job_qualification_invariant), "Cntr", all_items$is_job_qualification_invariant
)

all_items$is_team_invariant <- ifelse(
  all_items$is_team_invariant == "Sì" | all_items$is_team_invariant == "Si", 
  "Yes", all_items$is_team_invariant
)

all_items$is_team_invariant <- ifelse(
  is.na(all_items$is_team_invariant), "Cntr", all_items$is_team_invariant
)


```



```{r}
rw_df <- all_items |> 
  dplyr::filter(is_rescue_worker == "yes" & job_qualification != "non_rescue_worker")

```



```{r}
fm1 <- brm(
  class ~ job_qualification,
    # (gender + age + education + employment + job_qualification),
    # last_training + rate_of_activity + is_job_qualification_invariant + is_team_invariant),
  family = bernoulli(),
  backend = "cmdstanr",
  rw_df
)
```

```{r}
pp_check(fm1)
```

```{r}
summary(fm1)
```

```{r}
conditional_effects(
  fm1, "job_qualification"
)
```



```{r}
fm2 <- brm(
  class ~ gender + age + education,
  family = bernoulli(),
  backend = "cmdstanr",
  rw_df
)
```

```{r}
summary(fm2)
```


EOF -------------------


```{r}
suppressMessages(mod_1c_v1 <- estimate_profiles(df = lpa_df, n_profiles = 1:9,
models = 1))
```


```{r}
mod_1c_v1
```



```{r}
only_rw <- all_items |> 
  dplyr::filter(is_rescue_worker == "yes")

rw_df <- data.frame(
  # exogeneous vars
  neu = only_rw$neuroticism, 
  extra = only_rw$extraversion,
  open = only_rw$openness,
  agree = only_rw$agreeableness,
  consc = only_rw$conscientiousness,
  mpss = only_rw$mpss_tot,
  # mediators
  actcop = only_rw$active_coping,
  avocop = only_rw$avoidance_coping,
  scpos = only_rw$pos_self_compassion,
  scneg = only_rw$neg_self_compassion,
  # endogeneous vars
  iesr = only_rw$iesr_ts,
  ptgi = only_rw$ptgi_total_score
)
```


```{r}
mod1 <- iesr ~ serial_m(actcop, scneg) + mpss + covariates(neu, consc)
out1 <- test_mediation(mod1, data = rw_df, robust= FALSE)
```

```{r}
summary(out1)
```





```{r}
# mod_med <- '
# 
#   ptgi_total_score ~ neuroticism       
#   ptgi_total_score ~ extraversion      
#   ptgi_total_score ~ openness          
#   ptgi_total_score ~ agreeableness    
#   ptgi_total_score ~ conscientiousness
#   ptgi_total_score ~ mpss_tot         
#   
#   iesr_ts ~ neuroticism     
#   iesr_ts ~ extraversion       
#   iesr_ts ~ openness           
#   iesr_ts ~ agreeableness     
#   iesr_ts ~ conscientiousness 
#   iesr_ts ~ mpss_tot          
#   
#   active_coping ~ neuroticism       
#   active_coping ~ extraversion    
#   active_coping ~ openness        
#   active_coping ~ agreeableness   
#   active_coping ~ conscientiousness
#   active_coping ~ mpss_tot        
#   
#   avoidance_coping ~ neuroticism       
#   avoidance_coping ~ extraversion     
#   avoidance_coping ~ openness         
#   avoidance_coping ~ agreeableness    
#   avoidance_coping ~ conscientiousness
#   avoidance_coping ~ mpss_tot  
#   
#   ts_sc ~ neuroticism       
#   ts_sc ~ extraversion     
#   ts_sc ~ openness         
#   ts_sc ~ agreeableness    
#   ts_sc ~ conscientiousness
#   ts_sc ~ mpss_tot     
#   
#   ptgi_total_score ~ ts_sc
#   ptgi_total_score ~ active_coping
#   ptgi_total_score ~ avoidance_coping
#   
#   iesr_ts ~ ts_sc
#   iesr_ts ~ active_coping
#   iesr_ts ~ avoidance_coping
# '
```


```{r}
# mod_med <- '
# 
#   ptgi_total_score ~ c(gn1, gn2)*neuroticism + c(ge1, ge2)*extraversion + c(go1, go2)*openness + 
#                         c(ga1, ga2)*agreeableness + c(gc1, gc2)*conscientiousness + c(gm1, gm2)*mpss_tot + 
#                         c(gat1, gat2)*active_coping + c(gv1, gv2)*avoidance_coping
#                      
#   iesr_ts          ~ c(in1, in2)*neuroticism + c(ie1, ie2)*extraversion + c(io1, io2)*openness + 
#                         c(ia1, ia2)*agreeableness + c(ic1, ic2)*conscientiousness + c(im1, im2)*mpss_tot + 
#                         c(iat1, iat2)*active_coping + c(iv1, iv2)*avoidance_coping
#   
#   pos_self_compassion ~ c(pscn1, pscn2)*neuroticism + c(psce1, psce2)*extraversion + c(psco1, psco2)*openness + 
#                         c(psca1, psca2)*agreeableness + c(pscc1, pscc2)*conscientiousness + c(pscm1, pscm2)*mpss_tot + 
#                         c(psct1, psct2)*active_coping + c(pscv1, pscv2)*avoidance_coping
#     
#   neg_self_compassion ~ c(nscn1, nscn2)*neuroticism + c(nsce1, nce2)*extraversion + c(nsco1, nsco2)*openness + 
#                         c(nsca1, nsca2)*agreeableness + c(nscc1, nscc2)*conscientiousness + c(nscm1, nscm2)*mpss_tot + 
#                         c(nscat1, nsct2)*active_coping + c(nscv1, nscv2)*avoidance_coping 
# 
#   ptgi_total_score ~ c(gpsc1, gpsc2)*pos_self_compassion + c(gnsc1, gnsc2)*neg_self_compassion
#   iesr_ts          ~ c(ipsc1, ipsc2)*pos_self_compassion + c(insc1, insc2)*neg_self_compassion
#   
#   pos_self_compassion ~~ neg_self_compassion
#   
#   # indirect effect ()
#   abgg1 := pscn1*gpsc1 + psce1*gpsc1 + psco1*gpsc1 + psca1*gpsc1 + pscc1*gpsc1 + pscm1*gpsc1 + psct1*gpsc1 + pscv1*gpsc1 
#   abgg2 := pscn2*gpsc2 + psce2*gpsc2 + psco2*gpsc2 + psca2*gpsc2 + pscc2*gpsc2 + pscm2*gpsc2 + psct2*gpsc2 + pscv2*gpsc2 
#   
#   abig1 := pscn1*ipsc1 + psce1*ipsc1 + psco1*ipsc1 + psca1*ipsc1 + pscc1*ipsc1 + pscm1*ipsc1 + psct1*ipsc1 + pscv1*ipsc1 
#   abig2 := pscn2*ipsc2 + psce2*ipsc2 + psco2*ipsc2 + psca2*ipsc2 + pscc2*ipsc2 + pscm2*ipsc2 + psct2*ipsc2 + pscv2*ipsc2 
#   
#   # total effect
#   totalgg1 := abgg1 + gn1 + ge1 + go1 + ga1 + gc1 + gm1 + gat1 + gv1
#   totalgg2 := abgg2 + gn2 + ge2 + go2 + ga2 + gc2 + gm2 + gat2 + gv2
#   
#   totalig1 := abig1 + in1 + ie1 + io1 + ia1 + ic1 + im1 + iat1 + iv1
#   totalig2 := abig2 + in2 + ie2 + io2 + ia2 + ic2 + im2 + iat2 + iv2
#   
# '
```






```{r}
mod_med <- '

  ptgi_total_score ~ c(gn1, gn2)*neuroticism + c(ge1, ge2)*extraversion + c(go1, go2)*openness + 
                        c(ga1, ga2)*agreeableness + c(gc1, gc2)*conscientiousness + c(gm1, gm2)*mpss_tot 
                        
  iesr_ts          ~ c(in1, in2)*neuroticism + c(ie1, ie2)*extraversion + c(io1, io2)*openness + 
                        c(ia1, ia2)*agreeableness + c(ic1, ic2)*conscientiousness + c(im1, im2)*mpss_tot 
  
  
                        
  pos_self_compassion ~ c(pscn1, pscn2)*neuroticism + c(psce1, psce2)*extraversion + c(psco1, psco2)*openness + 
                        c(psca1, psca2)*agreeableness + c(pscc1, pscc2)*conscientiousness + c(pscm1, pscm2)*mpss_tot 
    
  neg_self_compassion ~ c(nscn1, nscn2)*neuroticism + c(nsce1, nsce2)*extraversion + c(nsco1, nsco2)*openness + 
                        c(nsca1, nsca2)*agreeableness + c(nscc1, nscc2)*conscientiousness + c(nscm1, nscm2)*mpss_tot 

  active_coping ~ c(acn1, acn2)*neuroticism + c(ace1, ace2)*extraversion + c(aco1, aco2)*openness + 
                        c(aca1, aca2)*agreeableness + c(acc1, acc2)*conscientiousness + c(acm1, acm2)*mpss_tot 
                        
  avoidance_coping ~ c(vcn1, vcn2)*neuroticism + c(vce1, vce2)*extraversion + c(vco1, vco2)*openness + 
                        c(vca1, vca2)*agreeableness + c(vcc1, vcc2)*conscientiousness + c(vcm1, vcm2)*mpss_tot 



  ptgi_total_score ~ c(gpsc1, gpsc2)*pos_self_compassion + c(gnsc1, gnsc2)*neg_self_compassion +
                     c(gac1, gac2)*active_coping + c(gav1, gav2)*avoidance_coping
                     
  iesr_ts          ~ c(ipsc1, ipsc2)*pos_self_compassion + c(insc1, insc2)*neg_self_compassion +
                     c(iac1, iac2)*active_coping + c(iav1, iav2)*avoidance_coping
  
  pos_self_compassion ~~ neg_self_compassion
  
  # indirect effect 
  abgg1 := pscn1*gpsc1 + psce1*gpsc1 + psco1*gpsc1 + psca1*gpsc1 + pscc1*gpsc1 + 
           pscm1*gpsc1 +
           nscn1*gpsc1 + nsce1*gpsc1 + nsco1*gpsc1 + nsca1*gpsc1 + nscc1*gpsc1 + 
           nscm1*gpsc1 +
           acn1*gpsc1 + ace1*gpsc1 + aco1*gpsc1 + aca1*gpsc1 + acc1*gpsc1 + 
           acm1*gpsc1 +
           vcn1*gpsc1 + vce1*gpsc1 + vco1*gpsc1 + vca1*gpsc1 + vcc1*gpsc1 + 
           vcm1*gpsc1 
           
  abgg2 := pscn2*gpsc2 + psce2*gpsc2 + psco2*gpsc2 + psca2*gpsc2 + pscc2*gpsc2 + 
           pscm2*gpsc2 +
           nscn2*gpsc2 + nsce2*gpsc2 + nsco2*gpsc2 + nsca2*gpsc2 + nscc2*gpsc2 +
           nscm2*gpsc2 +
           acn2*gpsc2 + ace2*gpsc2 + aco2*gpsc2 + aca2*gpsc2 + acc2*gpsc2 + 
           acm2*gpsc2 +
           vcn2*gpsc2 + vce2*gpsc2 + vco2*gpsc2 + vca2*gpsc2 + vcc2*gpsc2 + 
           vcm2*gpsc2 
   
   abig1 := pscn1*ipsc1 + psce1*ipsc1 + psco1*ipsc1 + psca1*ipsc1 + pscc1*ipsc1 + 
           pscm1*ipsc1 +
           nscn1*ipsc1 + nsce1*ipsc1 + nsco1*ipsc1 + nsca1*ipsc1 + nscc1*ipsc1 + 
           nscm1*ipsc1 +
           acn1*ipsc1 + ace1*ipsc1 + aco1*ipsc1 + aca1*ipsc1 + acc1*ipsc1 + 
           acm1*ipsc1 +
           vcn1*ipsc1 + vce1*ipsc1 + vco1*ipsc1 + vca1*ipsc1 + vcc1*ipsc1 + 
           vcm1*ipsc1 
                   
 abig2 := pscn2*ipsc2 + psce2*ipsc2 + psco2*ipsc2 + psca2*ipsc2 + pscc2*ipsc2 +  
          pscm2*ipsc2 +
          nscn2*ipsc2 + nsce2*ipsc2 + nsco2*ipsc2 + nsca2*ipsc2 + nscc2*ipsc2 +
          nscm2*ipsc2 +
          acn2*ipsc2 + ace2*ipsc2 + aco2*ipsc2 + aca2*ipsc2 + acc2*ipsc2 + 
          acm2*ipsc2 +
          vcn2*ipsc2 + vce2*ipsc2 + vco2*ipsc2 + vca2*ipsc2 + vcc2*ipsc2 + 
          vcm2*ipsc2 
                  
  
  # total effect
    totalgg1 := abgg1 + gn1 + ge1 + go1 + ga1 + gc1 + gm1 + gac1 + gav1
    totalgg2 := abgg2 + gn2 + ge2 + go2 + ga2 + gc2 + gm2 + gac2 + gav2
    
    totalig1 := abig1 + in1 + ie1 + io1 + ia1 + ic1 + im1 + iac1 + iav1
    totalig2 := abig2 + in2 + ie2 + io2 + ia2 + ic2 + im2 + iac2 + iav2
  
'
```

```{r}
all_items$neg_self_compassion <- -1 * all_items$neg_self_compassion 
```


```{r}
fit2 <- sem(mod_med, data = all_items, group = "is_rescue_worker", 
            se = "bootstrap",
           bootstrap = 5000,
           parallel ="snow", ncpus = 8)
```

```{r}
standardizedSolution_boot_ci(fit2)
```


```{r}
modificationindices(fit2, sort = TRUE)
```


```{r}
summary(fit2,  fit.measures=TRUE, standardized = TRUE)
```

```{r}
cor(
  cbind(
    all_items$pos_self_compassion,
    all_items$neg_self_compassion,
    all_items$ptgi_total_score,
    all_items$iesr_ts
  )
) |> round(2)
```

```{r}
library(semhelpinghands)

ci_boot <- standardizedSolution_boot_ci(fit2)
ci_boot
```



```{r}
parameterEstimates(fit2, boot.ci.type="bca.simple")
```


```{r}
lavaanPlot::lavaanPlot(model = fit2)
```


```{r}
fitMeasures(fit2)
```

